Effects of Weather on Maize Yield in Kenya

### 2019-01-17 presentations/January2019/presentation1.tex
slides making

Error structure, ARMA, AIC

@@

>>>>

\begin{itemize}
\item AIC
\item None of the random slopes significant
\item Group autocorrelation structure present

\begin{itemize}
\item Tested by the Lagrange multipliear test developed by Baltagi \& Li ($1991$; $1995$)
\item[$\boldsymbol{\rightarrow}$] The error structure modelled as ARMA($1$,$1$) 
\begin{itemize}
\item The preferred error structure found using AIC
\end{itemize}
\end{itemize}

@@

\note{
First set of fixed effects found- stepwise like procedure. Then test of significant of random slopes
\vspace{0.3cm}to verify: alternative step-down model building approach
using the Satterthwaites method to determine the p-values of the individual t-tests
